Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-11-04 ms.tex
showing the profile fitting results from the long multi-exposure time series

>>>>

Given how well the Line Intercept ratio between detectors 487 and 489 averages like $\sqrt{N}$ statistics in Figure \ref{fig:illumGradientChangeOverTime}, we look at the multi-exposure test to examine longer baselines.

\begin{figure*}
\gridline{\fig{ratio_for_AZLab06_Multi-Exposure_Baseline_487.pdf}{0.49\textwidth}{Ratio of the best fit line intercepts of 487 and 489 over the long multi-exposure test}}
\gridline{
\fig{allan_variance_for_AZLab06_Multi-Exposure_Baseline_487_intercepts.pdf}{0.49\textwidth}{Allan variance of the 487/489 ratio from the best-fit slope intercept}
\fig{all_var_azlab06_sub320_multi_exp_487_489_removelinear_True_489.pdf}{0.49\textwidth}{Allan variance of the 487/489 ratio from Aperture Photometry}
}
\caption{We repeat the experiment from Figure \ref{fig:illumGradientChangeOverTime} but this time over a long multi-exposure test. The line-fit method achieves worse results on short timescales but better results on long timescales.}\label{fig:illumGradientChangeOverTimeMultiExpBaseline}
\end{figure*}
